\section{Projects-Corporate/Commercial:}
	\begin{itemize}
		\item Setup Replication between a Percona slave and mysql master running on CentOS.

	 	\item Setting up, maintenance of svn repository for internal server tools codebase.
	 	
		\item Simple python script to update a given svn repo folder and reset the permissions on the contents.

	 	\item Module manager for importing and executing python modules from the filesystem,dynamically.

	 	\item Basic database test cases for a js driven,meta-data based web-app development framework
		
		\item Basic Selenium test cases for the js driven UI of the web-app framework.

		\item A python Package, to assign each user to a group, each of which has a specific set of permissions Create,Delete,Update,Migrate) of Machine Images,Volumes,Disks,Users,Cost limits,Applications etc. Used Django-ORM to store the tables on a MySQL DB.

		\item Scheduler-Job package A Wrapper(CmnScheduler,CmnJob,CmnPeriodicJob,CmnCronJob) around the python APScheduler library. The wrapper, has to receive a python function/object(which will inherit the CronJob/PeriodicJob class and override the run method) and run it in a seperate process and maintains a status table(running/finished/scheduled) of the process.(Also in the process found a bug in the apscheduler library and got it fixed)

		\item Sales order Upload: Sales order upload was a program that reads sales order headers and lines from an ASCII text file, sorts them according to the Sales order header and then creates/upgrades the sales order and lines table in Baan. The primary challenge was that there was no specific ordering/sequencing of the sales order lines and therefore all lines had to be read and sorted before updating the DB.

	 	\item Baan V Customization:Report Layout modification for Sales Invoice layout of Hungary,china,chile. As a consequence of the RoHS Guidelines ECR,there were a few fields that needed to be printed based on whether the RoHS flag was true or false. The key challenge was that Baan Reports had a limit of 128 fields that could be exported to the report. So had to write a couple of lines in the report script to get the required field from the table or calculate it if possible.

		\item Customization of Finance Transaction session: There were recurring problems of unbalanced transactions, due to a new sales order policy adopted.So customized the Finance Transaction session to allow upload of single transactions, currency-wise, thereby enabling the users to insert a transaction to balance the fiscal batch and close the year.
	\end{itemize}
